---
title: "Clase x. Redes Neuronales I"
author: "Diego Kozlowski y Juan Barriola"
date: "  "
output: 
  html_notebook: 
    toc: true
    toc_float: true
    depth: 2
---

# Fully connected layers

Vamos a utilizar la librería [__KERAS__](https://keras.rstudio.com/)

Getting Started

## instalación
Installation

First, install the keras R package from GitHub as follows:

The Keras R interface uses the TensorFlow backend engine by default. To install both the core Keras library as well as the TensorFlow backend use the install_keras() function:


```{r}

# devtools::install_github("rstudio/keras")
library(keras)
# install_keras()

```
This will provide you with default CPU-based installations of Keras and TensorFlow. If you want a more customized installation, e.g. if you want to take advantage of NVIDIA GPUs, see the documentation for install_keras().


```{r}
mnist <- dataset_mnist()
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y
```


```{r}
x_train[1,,]
```


```{r}
matrix.rotate <- function(img) { 
    t(apply(img, 2, rev))
}

par(mfrow=c(3, 3))
for (idx in 1:9) {
    label <- y_train[idx]
    image(matrix.rotate(x_train[idx,,]), col = grey(level = seq(1, 0, by=-1/255)), axes=F, main=label)
  
}
```

The x data is a 3-d array (images,width,height) of grayscale values . To prepare the data for training we convert the 3-d arrays into matrices by reshaping width and height into a single dimension (28x28 images are flattened into length 784 vectors). Then, we convert the grayscale values from integers ranging between 0 to 255 into floating point values ranging between 0 and 1:

```{r}
# reshape
x_train <- array_reshape(x_train, c(nrow(x_train), 784))
x_test <- array_reshape(x_test, c(nrow(x_test), 784))
# rescale
x_train <- x_train / 255
x_test <- x_test / 255
```


Note that we use the array_reshape() function rather than the dim<-() function to reshape the array. This is so that the data is re-interpreted using row-major semantics (as opposed to R’s default column-major semantics), which is in turn compatible with the way that the numerical libraries called by Keras interpret array dimensions.

The y data is an integer vector with values ranging from 0 to 9. To prepare this data for training we one-hot encode the vectors into binary class matrices using the Keras to_categorical() function:



```{r}
y_train <- to_categorical(y_train, 10)
y_test <- to_categorical(y_test, 10)
```


## Defining the Model


The core data structure of Keras is a model, a way to organize layers. The simplest type of model is the Sequential model, a linear stack of layers.

We begin by creating a sequential model and then adding layers using the pipe (%>%) operator:


```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', input_shape = c(784)) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 10, activation = 'softmax')
```



The input_shape argument to the first layer specifies the shape of the input data (a length 784 numeric vector representing a grayscale image). The final layer outputs a length 10 numeric vector (probabilities for each digit) using a softmax activation function.

Use the summary() function to print the details of the model:



```{r}
summary(model)
```

Next, compile the model with appropriate loss function, optimizer, and metrics:

```{r}
model %>% compile(
  loss = 'categorical_crossentropy',
  optimizer = optimizer_rmsprop(),
  metrics = c('accuracy')
)
```

## Training and Evaluation

Use the fit() function to train the model for 30 epochs using batches of 128 images:
```{r}
history <- model %>% fit(
  x_train, y_train, 
  epochs = 30, batch_size = 128, 
  validation_split = 0.2
)
```

The history object returned by fit() includes loss and accuracy metrics which we can plot:




```{r}
plot(history)
```


Evaluate the model’s performance on the test data:


```{r}
model %>% evaluate(x_test, y_test)
```

Generate predictions on new data:



```{r}
model %>% predict_classes(x_test)
```

Keras provides a vocabulary for building deep learning models that is simple, elegant, and intuitive. Building a question answering system, an image classification model, a neural Turing machine, or any other model is just as straightforward.



